Medical Concept Extraction

### 2012-12-16 paper/paper.tex
Fixing the acknowledgements
Normalizing the usage of libsvm, liblinear and crfsuite.

Our framework includes a model class that can be trained on certain data with certain features enabled. The model class supports training a libSVM, libLinear, and CRF classifier that can be used for prediction in the future. One of the nice things, about the model class is that it can be serialized and reloaded dynamically. This is a really nice capability because it allows you to train a large number of models on various subsets of the data and using various different features to see which perform the best.

@@

As mentioned previously, the framework's model class has support for training various classifiers: a Support Vector Machine, a CRF, and linear classifier. The implementation of these algorithms is delegates to various third-party libraries described below.

@@

\item {\tt models/<model-name>} - Contains the meta data specific to each model that was trained. The framework saves the model's internal state (the features used, the input test set, etc.) as well as the trained parameters for the libSVM, crfsuite, and libLinear classifiers. This information is used to deserialize and load a model at runtime for prediction tasks.

@@

\item {\tt liblinear} \cite{liblinear}: lib linear is a linear classifier library that has special support multi-class classification. It also provides easy to use training and predicting command line utilities that accept a similar input format as libsvm.

\item {\tt crfsuite} \cite{crfsuite}: crfsuite is an implementation for conditional random fields and includes command line front ends to train a model on data and to predict the labels on an unseen data set. The data format for the input training files is also a sparse matrix representation but is slightly different from the format used by libsvm and lib linear. Our codebase nicely abstracts out these format differences and produces the right format depending on the model in use.

@@

Found that libSVM was not worth while to use

@@

We sincerely thank Dr. Robert Berwick  and Geza Kovacs
for their guidance, help, and support.

>>>>

Our framework includes a model class that can be trained on certain data with certain features enabled. The model class supports training a libsvm, liblinear, and crfsuite classifiers that can be used for prediction in the future. One of the nice things, about the model class is that it can be serialized and reloaded dynamically. This is a really nice capability because it allows you to train a large number of models on various subsets of the data and using various different features to see which perform the best.

@@

As mentioned previously, the framework's model class has support for training various classifiers: a Support Vector Machine, a CRF, and L2-regularized Support Vector Machine. The implementation of these algorithms is delegates to various third-party libraries described below.

@@

\item {\tt models/<model-name>} - Contains the meta data specific to each model that was trained. The framework saves the model's internal state (the features used, the input test set, etc.) as well as the trained parameters for the libsvm, crfsuite, and liblinear classifiers. This information is used to deserialize and load a model at runtime for prediction tasks.

@@

\item {\tt liblinear} \cite{liblinear}: liblinear is a linear classifier library that has special support multi-class classification. It also provides easy to use training and predicting command line utilities that accept a similar input format as libsvm.

\item {\tt crfsuite} \cite{crfsuite}: crfsuite is an implementation for conditional random fields and includes command line front ends to train a model on data and to predict the labels on an unseen data set. The data format for the input training files is also a sparse matrix representation but is slightly different from the format used by libsvm and liblinear. Our codebase nicely abstracts out these format differences and produces the right format depending on the model in use.

@@

Found that libsvm was not worth while to use

@@

We sincerely thank Dr. Robert Berwick  and Geza Kovacs
for their guidance, help, and support. May the Force be with you,
always.
